### 2013-03-29 drafts/grammar/grammar.tex
Cleanup.
Added section in grammar.tex on online hierarchical program induction.

\usepackage{amsmath}
\usepackage{ amssymb }
\usepackage{graphicx}
\usepackage{syntax}
\usepackage{tikz}
\usepackage{tikz}
\usetikzlibrary{bayesnet}
\usetikzlibrary{arrows,automata, positioning, patterns,backgrounds}
\usetikzlibrary{arrows,shapes.gates.logic.US,shapes.gates.logic.IEC,calc}

@@

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

@@

>>>>

\usepackage{amsmath}
\usepackage{ amssymb }
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{syntax}
\usepackage{tikz}
\usetikzlibrary{bayesnet}
\usetikzlibrary{arrows,automata, positioning, patterns,backgrounds}
\usetikzlibrary{arrows,shapes.gates.logic.US,shapes.gates.logic.IEC,calc}

@@

\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

@@

\begin{algorithm}
\caption{Hierarchical program induction (E-C)}\label{alg:basic-progind}
\begin{algorithmic}[1]
\State  \textbf{Exploration step: } Let $F$ be a set of $T$ samples
  i.i.d from $p_{e|G}(\cdot | G^{(j)})$.
\State \textbf{Compression step: } 
\begin{align*}
G^{(j+1)}, \{e^{(j+1)}_i\} &= 
\argmax_{G, \{e_i | e_i \in F \}}
\sum_i \left( 
\log{p_{t|e}(t_i|e_i)}+ 
\log{p_{e|G}(e_i|G)} \right )\\
&+
\log{p_{G|\theta}(G|\theta)}
\end{align*}
\end{algorithmic}
\end{algorithm}

@@

\subsection{An online algorithm}

Here we present an online version of the algorithm that only chooses
an expression for each task once. We can view the problem as MAP
estimation of the unobserved variables in the following graphical
model:

\begin{figure}[h]
\begin{tikzpicture}[->, circle]

\node[obs] (theta) {$\theta$} ;
\node[latent, below=of theta] (G) {G} 
   child {node [latent] (e1) {$e_1$} 
      child {node [obs] (t1) {$t_1$}}}
   child {node [latent] (e2) {$e_2$} 
      child {node [obs] (t2) {$t_2$}}}
   child {node [latent] (e3) {$e_3$} 
      child {node [obs] (t3) {$t_3$}}}
   child {node [latent] (e4) {$e_4$} 
      child {node [obs] (t5) {$t_4$}}}
   child {node  (edots) {$\dots$} edge from parent[draw=none] 
      child {node  (tdots) {$\dots$} edge from parent[draw=none]}};

\edge {theta} {G};

\end{tikzpicture}
\end{figure}

We want to choose $e_i$ and $G$ to maximize our objective function. We
will perform the following iterative procedure. Given a current
setting of $G$, set $e_i$ to optimize the weights on the edges to
$t_i$ and $G$. Update $G$ to optimize the weight on the edge to
$\theta$ and all the edges to previous set expressions $e_j, j\leq
i$.

\begin{algorithm}
\caption{Online hierarchical program induction}\label{alg:online-progind}
\begin{algorithmic}
\State Initialize $G_0$.
\For{$i\gets 1, \dots$}
\State $e_i^* = \argmax_{e} \log p(t_i|e_i) + \log p(e_i|G_{i-1}) $
\State $G_i = \argmax_{G} \log p(G|\theta) + \sum_{j \leq i} \log p(e_i|G) $
\EndFor
\end{algorithmic}
\end{algorithm}
